Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-18 manuscript/supplemental_material.Rnw
move core placenta pathway analysis up
fix human lineage table label

<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=NA,
                                    caption="\\lineagetableexplanationtypeiii{\\human}{all other species}",
                                    label="tab:human_linage_specific_all"
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@

@@

@@

\subsection{Pathway Analysis}
\begin{table}
<<pathway_analysis,echo=FALSE,results="asis",cache.extra=file.info(dir("../data","placenta_gsea.*",full.names=TRUE))[,"mtime"]>>=
pathway <- list()
for (database in c("kegg","reactome","biocarta","netpath")) {
    load(paste0("../data/placenta_gsea_",database))
    eval(parse(text=paste0("gsea.table <- placenta_gsea_",database)))
    gsea.table[,Database:=gsub("^(.)","\\U\\1",database,perl=TRUE)]
    pathway[[database]] <-
        gsea.table
}
pathway.analysis <-
    rbindlist(pathway)[fdr < 0.1,]
rm(pathway)
pathway.analysis[,Pathway:=gsub("^(KEGG|BIOCARTA|REACTOME) ","",
                                gsub("_+"," ",
                                     Pathway))]
pathway.analysis[,Pathway:=gsub(".+\\%","",Pathway)]

>>>>

<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=NA,
                                    caption="\\lineagetableexplanationtypeiii{\\human}{all other species}",
                                    label="tab:human_lineage_specific_all"
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@

@@

\begin{table}
<<pathway_analysis,echo=FALSE,results="asis",cache.extra=file.info(dir("../data","placenta_gsea.*",full.names=TRUE))[,"mtime"]>>=
pathway <- list()
for (database in c("kegg","reactome","biocarta","netpath")) {
    load(paste0("../data/placenta_gsea_",database))
    eval(parse(text=paste0("gsea.table <- placenta_gsea_",database)))
    gsea.table[,Database:=gsub("^(.)","\\U\\1",database,perl=TRUE)]
    pathway[[database]] <-
        gsea.table
}
pathway.analysis <-
    rbindlist(pathway)[fdr < 0.1,]
rm(pathway)
pathway.analysis[,Pathway:=gsub("^(KEGG|BIOCARTA|REACTOME) ","",
                                gsub("_+"," ",
                                     Pathway))]
pathway.analysis[,Pathway:=gsub(".+\\%","",Pathway)]

@@
